%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contents: The title page
% $Id: title.tex,v 1.2 2002/05/26 22:44:33 zuohuijun Exp $
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifx\pdfoutput\undefined 
\else
\pdfbookmark{封面}{title}
\fi

\newlength{\centeroffset}
\setlength{\centeroffset}{-0.5\oddsidemargin}
\addtolength{\centeroffset}{0.5\evensidemargin}
\thispagestyle{empty}

\vspace{\stretch{2}}

\noindent\makebox[0pt][l]{\begin{minipage}{\textwidth}
\flushleft

{\huge \bfseries \R{} 导论}
\noindent\rule[-1ex]{\textwidth}{5pt}\\[2.5ex]
\flushright
\hfill\emph{\large 关于~\R{} 语言的注解：一个数据分析和图形显示的程序设计环境\\
英文版本 2.3.0 (2006-04-24)\\
中文版本 0.1 (2006-06-15)}

\end{minipage}}

\vfill

\noindent\makebox[0pt][l]{%
\begin{minipage}{\textwidth}{
\flushleft
W. N. Venables, D. M. Smith\\
R 核心开发小组（the R Development Core Team）\\
\noindent\rule[-1ex]{\textwidth}{2.5pt}\\[2.5ex]
}
\end{minipage}}

\pagebreak

\vspace{\stretch{2}}

\vfill

\begin{small}
\flushleft

\emph{英文文档的版权说明:}

Copyright \copyright 1990 W.~N.~Venables 

Copyright \copyright 1992 W.~N.~Venables \& D.~M.~Smith 

Copyright \copyright 1997 R.~Gentleman \& R.~Ihaka 

Copyright \copyright 1997, 1998 M.~Maechler 

Copyright \copyright 1999C2006 R Development Core Team

Permission is granted to make and distribute verbatim copies of this
manual provided the copyright notice and this permission notice are
preserved on all copies.

Permission is granted to copy and distribute modified versions of this
manual under the conditions for verbatim copying, provided that the
entire resulting derived work is distributed under the terms of a
permission notice identical to this one.

Permission is granted to copy and distribute translations of this manual
into another language, under the above conditions for modified versions,
except that this permission notice may be stated in a translation
approved by the R Development Core Team.

\vspace{2ex}
\emph{参考译文如下（具体以英文原文为准）：}

版权  \copyright 1990 W.~N.~Venables               
                                                   
版权  \copyright 1992 W.~N.~Venables \& D.~M.~Smith 
                                                   
版权  \copyright 1997 R.~Gentleman \& R.~Ihaka      
                                                   
版权  \copyright 1997, 1998 M.~Maechler            
                                                   
版权  \copyright 1999C2006 R Development Core Team

在遵守并包含本文档版权声明的前提下，制作和发布本文档的完整拷贝是允许的。
并且，所有这些拷贝均受到本许可声明的保护。

在遵守上述完整拷贝版本有关版权声明的前提下，拷贝和发布基于本文档完整
拷贝的修改版本是允许的，并且，发布所有通过修改本文档而得到的工作成果，
须使用与本文档的许可声明一致的许可声明。

在遵守上述修改版本版权声明的前提下，拷贝和发布本文档其它语言的翻译版本
是允许的，如果本许可声明有经 R 核心开发小组（R Development Core Team）核
准的当地化译本，则遵循当地化译本。

\vspace{2ex}
\emph{关于本中文翻译文档的版权声明：}

本文档为自由文档（GNU FDL），
在GNU自由文档许可证（\url{http://www.gnu.org/copyleft/fdl.html}）下发布，
不明示或者暗示有任何保证。本文档可以自由复制，修改，散布，但请保留使用
许可声明。

\end{small}


\endinput
